---
title: "1.2 Descriptive Statistics & Graphs"
author: "SY"
date: "2023-02-15"
output:
  html_document: default
  word_document: default
  pdf_document: default
---

"Frequency Distributions, Skewness and Kurtosis, Histogram, Pie Chart & Bar Chart" - Examines one variable at a time.



Initial Configurations

1. Import .sav file into RStudio

```{r}

```

Frequency Distributions and Histograms:

2. Create a histogram for the values of the variable ztotmen 

```{r}

```

Histogram with no. of bins changed using breaks.


```{r}

```


3. Calculate the mean and median for ztotmen

```{r}

```


4. Describe the variable ztotmen

```{r}

```

5. Create a histogram for ztotmen and mark the mean and median in that.

```{r}


```


Histogram for Subset of Data:


6. Create the histogram for the subsetted data of ztotmen less than 200.

```{r}



```


Skewness and Kurtosis: 
These are about the overall shape of an ordinal or scale level variables. It is irrelevant for nominal variables.


7. Create a histogram for zallpte


```{r}


```

To determine whether the skewness and kurtosis levels are excessively problematic, there are couple of ways.

- Cutoff of +-0.700 (If the skewness and Kurtosis is greater than 0.700 or less than -0.700 then they are unacceptable / problematic)

-  Skewness statistic divided by the standard error of the skewness statistic and
Kurtosis statistic divided by the standard error of the kurtosis statistic. If the resultant numbers are beyond +-1.96 then we can assume that the distribution suffers from "significant" skewness and/or kurtosis.

Thus, here the variable "how long this workplace is in operation" is said to be excessively positively skewed and leptokurtic.


Bar Charts and Pie Charts:

8. Create a pie chart for kactivm1

8.1 Remove the NA values from kactivm1

8.2 Convert that into data frame

8.3 Describe the variable kactivm1 after removing NA values.

8.4 Create the frequency and cumulative frequency table for kactivm1


8.5 Create a pie chart for kactivm1 with those values.

```{r}


```

9. Create a barplot for kactivm1

```{r}

```


It is good to spend some time for "getting to know" our data and variables. We should always request frequency distributions and histograms for every single variable we plan to model: nominal, ordinal & scale. Have a look at how the responses are distributed and what the distributions look like graphically. 

Then only for our ordinal and scale-level variables, we have to ask for parametric statistics.

"Parametric statistics" are those statistics for which the mean and standard deviation are relevant.

"Nonparametric statistics" are reserved for the analysis of nominal variables where the mean and standard deviation are not at all meaningful statistics. 

The relevant parametric statistics we should request for ordinal and scale-level variables include the mean, median, standard deviation, minimum, maximum, range, skewness, and kurtosis. 
The only nonparametric statistic we really need to look at for nominal variables is the mode.















