---
title: '1.1 Descriptive Statistics: Central Tendency and Measures of Dispersion'
author: "RUTHRESHWARAN M"
date: "2023-02-15"
output:
  pdf_document: default
  word_document: default
  html_document: default
---
"Central Tendency and Measures of dispersion"
- Examines one variable at a time.


1. Import .sav file into RStudio

```{r}
library(tidyverse)
library(haven)
rd<-read_sav("Raw/chap3data.sav")
rd

```

Measures of Central Tendency: Focuses on the center of a distribution / looks inward.

Mean : relevant for ordinal and scale level variables

2. Print the values of the zadm_tot variable in the given data set and write your understanding about the type of variable.

```{r}
rd$zadm_tot

```
THis is a Scalable Variable.

3. Calculate the mean for the values of zadm_tot as it is and observe the output.

```{r}
mean(rd$zadm_tot)
```


4. Remove the missing values values from the zadm_tot and then calculate the mean.

```{r}
rwd<-rd%>%filter(zadm_tot>=0)
mean(rwd$zadm_tot)
```

Median: relevant for ordinal and scale level variables


5. Calculate Mean & Median for some variable in the data set and check whether replacing 0 for missing values makes sense.


```{r}

```

6. Calculate the Mean & Median for the above variable (after filtering NA)

```{r}


```

Mode: most suitable even for nominal variables.


Frequency Table:

7. Create the frequency table for the variable kactivm1
```{r}
frequency_table<-table(rd$kactivm1)
frequency_table

```

Cumulative Frequency Table:

8. Create the cumulative frequency table for kactivm1.

```{r}
cumsum(frequency_table)

```

Relative Frequency Table: 

9. Create the relative frequency table for kactivm1.

```{r}
prop.table(frequency_table)

```


R doesn't have the inbuilt mode function. So here we write a user defined function for mode. 

10. Calculate the mode for kactivm1.

```{r}
calc_mode<-function(ds1){
  uniqds1<-unique(ds1)
  uniqds1[which.max(tabulate(match(ds1,uniqds1)))]
}
calc_mode(rd$kactivm1)

```


Measures of Dispersion: focuses on the amount of "spread" across a distribution / looks outward. It is irrelevant for nominal variables.

Range and Standard Deviation: relevant for ordinal and scale level variables
Range: max value - min value

Standard Deviation: Average Variability. It takes into account every single observation and its relationship with the mean.

11. Calculate the standard deviation for the variable ztotmen.
```{r}
sd(rd$ztotmen)


```

12. Calculate the summary statistics for the variable ztotmen.
```{r}

summary(rd$ztotmen)
```

13. Calculate the descriptive statistics using describe function for ztotmen.


```{r}
library(psych)
describe(rd$ztotmen)

```

14. Write your interpretation/understanding about the above analysis.

     









